Meta-analysis on Sex*Dianosis interaction in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-09-02 individual-cohorts/meta_analysis/meta-analysis_interaction.Rmd
Initial commit

---
title: "Meta-analysis on diagnosis in MSSM-Penn-Pitt and HBCC ACC/DLPFC"
author: "KM and GH"
date: "`r date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r knit2synapse, eval=FALSE, echo=FALSE}
# rmarkdown::render("individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd")

@@

createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on diagnosis',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

```{r synapse.parameters, include=FALSE, cache=FALSE, eval=TRUE}
thisFileName <- 'meta-analysis_diagnosis.Rmd'

@@

```{r input_data}
mpp_acc <- readr::read_tsv(synGet("syn22079117")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )

mpp_dlpfc <- readr::read_tsv(synGet("syn22079472")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )

@@

hbcc_dlpfc <- readr::read_tsv(synGet("syn22084205")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )
Ids <- c("syn22079117", "syn22079472", "syn22086829", "syn22084205")
```

@@

```{r store, eval=TRUE}
# Code
CODE <- Folder(name = "Meta-analysis on diagnosis", parentId = "syn22315403") # Make sure these match the folder name and parent Id in the first chunk.
CODE <- synStore(CODE)

# Store meta-analysis
res_dlpfc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_dlpfc_diagnosis_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_dlpfc_diagnosis_meta_analysis.tsv', 
                name = 'diagnosis Normalised, meta-analysis (DLPFC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
res_acc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_acc_diagnosis_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_acc_diagnosis_meta_analysis.tsv', 
                name = 'diagnosis Normalised, meta-analysis (ACC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
```

>>>>

---
title: "Meta-analysis on Sex*Dianosis interaction in MSSM-Penn-Pitt and HBCC ACC/DLPFC"
author: "KM and GH"
date: "`r date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r knit2synapse, eval=FALSE, echo=FALSE}
# rmarkdown::render("individual-cohorts/meta_analysis/meta-analysis_interaction.Rmd")

@@

createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_interaction.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on Sex*Diagnosis interaction',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

```{r synapse.parameters, include=FALSE, cache=FALSE, eval=TRUE}
thisFileName <- 'meta-analysis_interaction.Rmd'

@@

```{r input_data}
mpp_acc <- readr::read_tsv(synGet("syn22276990")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )

mpp_dlpfc <- readr::read_tsv(synGet("syn22277179")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )

@@

hbcc_dlpfc <- readr::read_tsv(synGet("syn22280364")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) %>% getGeneSymbol( 'gene_id' )

Ids <- c("syn22276990", "syn22277179", "syn22086829", "syn22280364")
```

@@

```{r store, eval=FALSE}
# Code
CODE <- Folder(name = "Meta-analysis on Sex*Diagnosis interaction", parentId = "syn22315403") # Make sure these match the folder name and parent Id in the first chunk.
CODE <- synStore(CODE)

# Store meta-analysis
res_dlpfc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_dlpfc_interaction_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_dlpfc_interaction_meta_analysis.tsv', 
                name = 'Interaction meta-analysis (DLPFC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
res_acc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_acc_Interaction_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_acc_Interaction_meta_analysis.tsv', 
                name = 'Interaction meta-analysis (ACC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
```
